HTW EXAM sims

### 2023-11-09 Simulations/htw_exam.qmd
plotting model predictions

a_testOnly=list(pred_dat="test_avg",pred_fun="alm.responseOnly",loss_fun="RMSE",loss_data="test_error")
a_trainOnly=list(pred_dat="test_avg",pred_fun="alm.responseOnly",loss_fun="RMSE",loss_data="train_error")
a_testTrain=list(pred_dat="test_avg",pred_fun="alm.responseOnly",loss_fun="RMSE",loss_data="test_error+train_error")

e_testOnly=list(pred_dat="test_avg",pred_fun="exam.response",loss_fun="RMSE",loss_data="test_error")
e_trainOnly=list(pred_dat="test_avg",pred_fun="exam.response",loss_fun="RMSE",loss_data="train_error")
e_testTrain=list(pred_dat="test_avg",pred_fun="exam.response",loss_fun="RMSE",loss_data="test_error+train_error")

h_testOnly=list(pred_dat="test_avg",pred_fun="predict_alm_exam_weighted_hybrid",loss_fun="RMSE",loss_data="test_error")
h_trainOnly=list(pred_dat="test_avg",pred_fun="predict_alm_exam_weighted_hybrid",loss_fun="RMSE",loss_data="train_error")
h_testTrain=list(pred_dat="test_avg",pred_fun="predict_alm_exam_weighted_hybrid",loss_fun="RMSE",loss_data="test_error+train_error")

hybrid_te_v <- wrap_grid(vAvg, c_values, lr_values, input.layer, output.layer,predParams=e_testOnly)
hybrid_tetr_v <- wrap_grid(vAvg, c_values, lr_values, input.layer, output.layer,predParams=e_testTrain)
hybrid_tr_v<- wrap_grid(vAvg, c_values, lr_values, input.layer, output.layer,predParams=e_trainOnly)

```{r}
plan(multisession)

@@

list2env(readRDS(here::here("data/model_cache/con_group_exam_fits.rds")), envir = .GlobalEnv)
list2env(readRDS(here::here("data/model_cache/var_group_exam_fits.rds")), envir = .GlobalEnv)

@@

>>>>

@@

list2env(readRDS(here::here("data/model_cache/con_group_exam_fits.rds")), envir = .GlobalEnv)
list2env(readRDS(here::here("data/model_cache/var_group_exam_fits.rds")), envir = .GlobalEnv)
list2env(readRDS(here::here("data/model_cache/hybrid_group_exam_fits.rds")), envir = .GlobalEnv)

@@

almParams <- cbind(Model="ALM_Test_Only",pluck(a_te_v, "Fit"), pluck(a_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)) ) |>
  rbind(cbind(Model="ALM Test and Train", pluck(a_tetr_v,"Fit"), pluck(a_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="ALM Train Only", pluck(a_tr_v, "Fit"), pluck(a_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))))

examParams <- cbind(Model="EXAM_Test_Only",pluck(ex_te_v, "Fit"), pluck(ex_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="EXAM Test and Train", pluck(ex_tetr_v,"Fit"), pluck(ex_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="EXAM Train Only", pluck(ex_tr_v, "Fit"), pluck(ex_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))))

hybridParams <-cbind(Model="Hybrid_Test_Only",pluck(hybrid_te_v, "Fit"), pluck(hybrid_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="HybridTest and Train", pluck(hybrid_tetr_v,"Fit"), pluck(hybrid_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="Hybrid Train Only", pluck(hybrid_tr_v, "Fit"), pluck(hybrid_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))))

pander("ALM") + pander(almParams) +
  pander("EXAM")+ pander(examParams)+
  pander("Hybrid")+ pander(hybridParams)

## Hybrid
```{r}
vte <- pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model,col=Model,shape=Model)) +geom_point() + 
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test Only")

vtetr <- pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model,col=Model,shape=Model)) +geom_point() + 
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test and Train")

vtetr <- pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model,col=Model,shape=Model)) +geom_point(alpha=.5) + 
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test and Train")

####

 pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity")
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test Only")

  pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity")
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test Only")

  pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Optimize for Test Only")
